Eval expressions

### 2021-02-09 analysis/expressions.Rmd
Use the correct function name for the match.call pattern

What function is evaled in this pattern
```{r}
E_match.call %>% group_by(match.call) %>% summarize(n = n_distinct(src_ref)) %>% arrange(desc())
```

>>>>

What function is evaled in this pattern
```{r}
E_match.call %>% group_by(func) %>% summarize(n_call_sites = n_distinct(src_ref)) %>% arrange(desc(n_call_sites))
```
